### 2005-11-10 doc/EFA/efa.tex
*** empty log message ***

 Let $Z^{AB}$ denote the common variables of $X^{A}$ and $X^{B}$, and let $Z^A$
and $Z^B$ be the distinct variables of $X^{A}$ and $X^{B}$,
respectively. We define the integer variables $Z$ of the
synchronous product of $A$ and $B$ as the vector $Z=(Z^A, Z^{AB},
Z^B)$. The guard functions $g_{q \sigma}(Z)$ are defined as
\begin{eqnarray}\label{guard_sync_1}
g_{q \sigma}(Z)=\left\{
\begin{array}{ll}
g_{q^A\sigma}(X^{A})\wedge g_{q^B\sigma}(X^{B}) \textrm{ if }\sigma\in \Sigma^A \cap \Sigma^B\\
g_{q^A\sigma}(X^{A}) \quad\quad \textrm{ if } \sigma\in \Sigma^A \setminus \Sigma^B\\
g_{q^B\sigma}(X^{B}) \quad\quad \textrm{ if }
\sigma\in\Sigma^B\setminus \Sigma^A
\end{array}\right.
\end{eqnarray}
If any one of the guards functions in the above definition are
undefined the guard function for the product $g_{q \sigma}$ is
also undefined. To simplify the notation further, we use "dummy"
guard functions in the following way. If $\sigma\in \Sigma^A
\setminus \Sigma^B$ we introduce fictional guards functions
$g_{q^B\sigma}(.)=1$ for $B$ and if $\sigma\in\Sigma^B\setminus
\Sigma^A$ we set $g_{q^A\sigma}(.)=1$. With this convention we can
write equation (\ref{guard_sync_1}) as
\begin{eqnarray}
g_{q \sigma}(Z)= g_{q^A\sigma}(X^{A})\wedge g_{q^B\sigma}(X^{B}).
\end{eqnarray}
To define the action functions for $A||B$ we look at the
restrictions of the updating functions $a^A_\delta$ and
$a^B_\delta$ to the sets $Z^A$ and $Z^B$. The updating functions
are defined as (if $X^{A}$ and $X^{B}$ have no common variables
then $Z^A=X^{A}$ and $Z^B=X^{B}$)
\begin{eqnarray}
a_{q \sigma}(Z)=\left\{
\begin{array}{ll}
 \big(a^A_{q^A \sigma}(X^{A}), a^B_{q^B \sigma}(Z^{B})\big)\quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
\big(a^A_{q^A \sigma}(X^{A}), Z^{B}\big)\quad\quad\quad\sigma\in \Sigma^A \setminus \Sigma^B\\
\big(Z^{A}, a^B_{q^B \sigma}(X^{B})\big)\quad\quad\quad\sigma\in
\Sigma^B \setminus \Sigma^A
\end{array}\right.
\end{eqnarray}
As in the definition of the guard functions the notion of being
undefined is inherited from the action functions of $A$ and $B$.
Similar to the "dummy" guard functions we introduce fictional
action functions. If $\sigma\in \Sigma^A \setminus \Sigma^B$ we
introduce fictional action functions $a_{q^B\sigma}(X^B)=X^B$ for
$B$ and if $\sigma\in\Sigma^B\setminus \Sigma^A$ we set
$a_{q^A\sigma}(X^A)=X^A$. If $X^{A}$ and $X^{B}$ have no common
variables then the formula for the action functions of the product
simplifies to
\begin{eqnarray}
a_{q \sigma}(Z)=
 \big(a^A_{q^A \sigma}(X^{A}), a^B_{q^B \sigma}(X^{B})\big).
\end{eqnarray}

>>>>

 Let $Z^{AB}$ denote the common variables of $X^{A}$ and $X^{B}$, and let $Z^A$
and $Z^B$ be the distinct variables of $X^{A}$ and $X^{B}$,
respectively. We define the integer variables $Z$ of the
synchronous product of $A$ and $B$ as the vector $Z=(Z^A, Z^{AB},
Z^B)$. The guard functions $g_{q \sigma}(Z)$ are defined as
\begin{eqnarray}\label{guard_sync_1}
g_{q \sigma}(Z)=\left\{
\begin{array}{ll}
g_{q^A\sigma}(X^{A})\wedge g_{q^B\sigma}(X^{B}) \textrm{ if }\sigma\in \Sigma^A \cap \Sigma^B\\
g_{q^A\sigma}(X^{A}) \quad\quad \textrm{ if } \sigma\in \Sigma^A \setminus \Sigma^B\\
g_{q^B\sigma}(X^{B}) \quad\quad \textrm{ if }
\sigma\in\Sigma^B\setminus \Sigma^A
\end{array}\right.
\end{eqnarray}
If any one of the guards functions in the above definition are
undefined the guard function for the product $g_{q \sigma}$ is
also undefined. To simplify the notation further, we use "dummy"
guard functions in the following way. If $\sigma\in \Sigma^A
\setminus \Sigma^B$ we introduce fictional guards functions
$g_{q^B\sigma}(.)=1$ for $B$ and if $\sigma\in\Sigma^B\setminus
\Sigma^A$ we set $g_{q^A\sigma}(.)=1$. With this convention we can
write equation (\ref{guard_sync_1}) as
\begin{eqnarray}
g_{q \sigma}(Z)= g_{q^A\sigma}(X^{A})\wedge g_{q^B\sigma}(X^{B}).
\end{eqnarray}
To define the action functions for $A||B$ we look at the
restrictions of the updating functions $a^A_\delta$ and
$a^B_\delta$ to the sets $Z^A$ and $Z^B$. The updating functions
are defined as (if $X^{A}$ and $X^{B}$ have no common variables
then $Z=(X^{A},X^{B})$)
\begin{eqnarray}\label{action_sync_1}
a_{q \sigma}(Z)=\left\{
\begin{array}{ll}
 \big(a^A_{q^A \sigma}(X^{A}), a^B_{q^B \sigma}(Z^{B})\big)\quad\quad\sigma\in \Sigma^A \cap \Sigma^B\\
\big(a^A_{q^A \sigma}(X^{A}), Z^{B}\big)\quad\quad\quad\sigma\in \Sigma^A \setminus \Sigma^B\\
\big(Z^{A}, a^B_{q^B \sigma}(X^{B})\big)\quad\quad\quad\sigma\in
\Sigma^B \setminus \Sigma^A
\end{array}\right.
\end{eqnarray}
As in the definition of the guard functions the notion of being
undefined is inherited from the action functions of $A$ and $B$.
Similar to the "dummy" guard functions we introduce fictional
action functions. If $\sigma\in \Sigma^A \setminus \Sigma^B$ we
introduce fictional action functions $a_{q^B\sigma}(X^B)=X^B$ for
$B$ and if $\sigma\in\Sigma^B\setminus \Sigma^A$ we set
$a_{q^A\sigma}(X^A)=X^A$. If $X^{A}$ and $X^{B}$ have no common
variables then equation (\ref{action_sync_1}), that defines the
action functions of the product, simplifies to
\begin{eqnarray}
a_{q \sigma}(Z)=
 \big(a^A_{q^A \sigma}(X^{A}), a^B_{q^B \sigma}(X^{B})\big).
\end{eqnarray}
